---
title: "Cohorts"
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(plotly)
library(gt)

df <- 
  readRDS("all_cohort_data_copy")
```


## Introduction

Hack.Diversity has had `r df |> distinct(year) |> nrow()` program cycles, with its first cohort beginning in `r min(df$year)`. Hack.Diversity has since welcomed over `r df |> nrow()` Fellows into the program with the `r max(df$year)` program welcoming `r df |> filter(year==max(year)) |> nrow()` Fellows with `r df |> filter(year==max(year), site=="Boston") |> nrow()` in **Boston** and `r df |> filter(year==max(year), site=="New York") |> nrow()` in **New York**.

```{r}
#| label: Cohort Size over the years
#| echo: false

p <- 
  df |> 
  group_by(year, site) |> 
  summarize(count = n(), 
            .groups = "drop") |> 
  ggplot(aes(x = year, y = count, color = site)) +
  geom_point() + 
  geom_line() + 
  scale_color_manual(values = c("dodgerblue4", "firebrick2")) + 
  scale_x_continuous(breaks = seq(2017, 2024, 1)) + 
  # geom_text(aes(label = count), color = "black", size = 3, 
  #           vjust = 1.75) + 
  labs(x = "Year", 
       y = "Count", 
       color = "Site", 
       title = "Hack.Diversity Fellow Cohort Size") +
  theme_bw()

ggplotly(p)


```

